---
title: "Preliminary bio-bibliography"
author:  | 
  | Robert Heilmayr
  | Assistant Professor V
  | University of California, Santa Barbara
date:    | 
  <!-- | Filed on: `r format(Sys.time(), '%B %d, %Y')` -->
  | Filed on: April 22, 2023
  | Last update filed on: June 30, 2021
  | This update refers to the period: July 1, 2021 to June 30, 2023
output: pdf_document
header-includes:
  - \usepackage{colortbl}
  - \usepackage{needspace}
  - \usepackage[explicit,pagestyles]{titlesec}
  - \titleformat{\section}{\needspace{5em}\Large\bfseries}{\thesection}{1em}{#1}[]
  - \titleformat{\subsection}{\needspace{5em}\large\bfseries}{\thesubsection}{1em}{#1}[]
  - \titleformat{\subsubsection}{\needspace{5em}\normalsize\bfseries}{\thesubsubsection}{1em}{#1}[]   
subparagraph: yes
geometry: margin=1in

# | This update refers to the period: September 16, 2017 to `r format(Sys.time(), '%B %d, %Y')`


---
```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(kableExtra)
library(magrittr)
library(readxl)
library(scales)

data_dir  <- 'D:/dev/biobib/data/'
na_replace <- function(table) {
  table <- table %>% 
    replace(is.na(.), "")
  return(table)
}

page_width <- round((6.5 / 0.13837) - 8) # Convert page width to em and reduce a bit for padding

# mutate_cond <- function(.data, condition, ..., new_init = NA, envir = parent.frame()) {
#   # Initialize any new variables as new_init
#   new_vars <- substitute(list(...))[-1]
#   new_vars %<>% sapply(deparse) %>% names %>% setdiff(names(.data))
#   .data[, new_vars] <- new_init
# 
#   condition <- eval(substitute(condition), .data, envir)
#   .data[condition, ] <- .data %>% filter(condition) %>% mutate(...)
#   .data
# }

research <- read_excel(paste0(data_dir, '1_research/research.xlsx'))

students <- read_excel(paste0(data_dir, '2_teaching/students.xlsx'))
teaching <- read_excel(paste0(data_dir, '2_teaching/teaching.xlsx'))
guest_lectures <- read_excel(paste0(data_dir, '2_teaching/guest_lectures.xlsx'))
gps <- read_excel(paste0(data_dir, '2_teaching/gps.xlsx'))
mentoring <- read_excel(paste0(data_dir, '2_teaching/mentoring.xlsx'))

grants <- read_excel(paste0(data_dir, '3_professional/grants.xlsx'))  ## to update
lectures <- read_excel(paste0(data_dir, '3_professional/lectures.xlsx'))
reviewing <- read_excel(paste0(data_dir, '3_professional/reviewing.xlsx'))
appointments <- read_excel(paste0(data_dir, '3_professional/appointments.xlsx'))
organizing <- read_excel(paste0(data_dir, '3_professional/organizing.xlsx'))
patents <- read_excel(paste0(data_dir, '3_professional/patents.xlsx'))


university <- read_excel(paste0(data_dir, '4_service/university.xlsx'))
# public <- read_csv(paste0(data_dir, '4_service/public.csv'))
public_writing <- read_excel(paste0(data_dir, '4_service/public_writing.xlsx'))
media <- read_excel(paste0(data_dir, '4_service/media.xlsx'))

rperiod = 4
```

# Curriculum vitae
## Education
Stanford University, Ph.D., Environment and Resources, 2016 \newline
Stanford University, M.A., Economics, 2014 \newline
Claremont McKenna College, B.A., Environmental Studies, Economics and Politics; Politics, Philosophy and Economics, 2006

## Areas of specialization
Environmental economics; Ecological economics; Land system science; Remote sensing; Geography; Conservation biology

## Previous and currently held academic or professional appointments
2017 - Present, Assistant Professor, University of California, Santa Barbara, Bren School of Environmental Science and Managment \newline
2016 - Present, Assistant Professor, University of California, Santa Barbara, Environmental Studies Program \newline
2016, Postdoctoral Fellow, University of Hawaii, MÄnoa, Department of Natural Resources and Environmental Management

## Professional organizations
American Economic Association \newline
Association of Environmental and Resource Economists \newline
Global Land Programme \newline

\newpage

# Part I. Research
## Cumulative list of publications
```{r research, echo=FALSE}
research[research$N.==15,] %<>% mutate(Authors = Authors %>% 
                                         str_replace("Carlson", "Carlson$^{\\\\dagger}$") %>%
                                         str_replace("Heilmayr", "Heilmayr$^{\\\\dagger}$")) 

research <- research %>% 
  mutate(Year = as.character(Year))

research$Publisher <- research %>%
  mutate(journal = str_c("\\textit{", research$journal, "}")) %>%
  select(journal, publisher, issue) %>%
  apply(1, function(x) paste(na.omit(x), collapse=", "))

research <- research %>%
  mutate(Title = ifelse(Category=="Book", 
                        str_c("\\textit{", Title, '}'),
                        str_c("``", Title, "''")),
         `Title and authors` = ifelse(is.na(temp_link),
                                      str_c(Title, ", ", Authors),
                                      str_c("\\href{", temp_link, "}{", Title, " ", Authors, "}")),
         `N.` = as.character(`N.`))

research[research$prev_status==3,] %<>% mutate(N. = paste0(N., "*")) 
research[research$prev_status==2,] %<>% mutate(N. = paste0(N., "**")) 
research[research$prev_status==1,] %<>% mutate(N. = paste0(N., "***")) 

published <- research %>% 
  filter(current_status==4)

new_row <- published %>%
  mutate(id = row_number()) %>%
  filter(review_period == rperiod) %>%
  select(id) %>%
  first() %>% 
  first()
old_row <- new_row - 1
  


published <- published %>%
  select("N.", "Year", "Title and authors", "Publisher", "Category")

published <- published %>%
  add_row(tibble_row(`N.` = "", `Year` = "", `Title and authors` = "", 
          `Publisher` = "added since last review", `Category` = ""), .after = old_row[[1]])



# published <- published %>% 
#   filter(N. != "18***")
published %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, escape = FALSE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  # kable_styling(latex_options = "striped") %>% 
  column_spec(c(1), width = "2em") %>%
  column_spec(c(2), width = "3em") %>%
  column_spec(c(3), width = "21em") %>%
  column_spec(c(4), width = "10em") %>%
  column_spec(c(5), width = "3em") %>%
  row_spec(c(old_row[[1]]), extra_latex_after = "\\noalign{\\global\\arrayrulewidth=0.6mm}\\arrayrulecolor{red}\\cline{1-5}") %>%
  row_spec(row = new_row[[1]], color = "red", font_size = 8, extra_latex_after = "\\arrayrulecolor{black}") %>%
  footnote(symbol =  c("Previously listed as work in press", "Previously listed as work submitted",
                       "Previously listed as work in progress", "Denotes equal contribution"), 
           symbol_manual = c("*", "**", "***", "$\\\\dagger$"))
```
## Work in press
```{r inpress, echo=FALSE}
inpress <- research %>%
  filter(current_status==3)

inpress <- inpress %>%
  select("N.", "Year", "Title and authors", "Publisher", "Category")
inpress %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, escape = FALSE, linesep = "") %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  column_spec(c(1), width = "2em") %>%
  column_spec(c(2), width = "3em") %>%
  column_spec(c(3), width = "23em") %>%
  column_spec(c(4), width = "12em") %>%
  column_spec(c(5), width = "3em") %>%
  footnote(symbol =  c("Previously listed as work in press", "Previously listed as work submitted",
                     "Previously listed as work in progress", "Denotes equal contribution"),
         symbol_manual = c("*", "**", "***", "$\\\\dagger$"))
```

<!-- ## Work submitted -->
<!-- ```{r submitted, echo=FALSE} -->
<!-- submitted <- research %>%  -->
<!--   filter(current_status==2) -->

<!-- submitted <- submitted %>% -->
<!--   select("N.", "Title and authors", "Publisher", "Category") -->
<!-- submitted %>% -->
<!--   kable("latex", booktabs = TRUE, longtable = TRUE, escape = FALSE, linesep = "\\addlinespace") %>% -->
<!--   kable_styling(latex_options = c("repeat_header")) %>% -->
<!--   column_spec(c(1), width = "2em") %>% -->
<!--   column_spec(c(2), width = "22em") %>% -->
<!--   column_spec(c(3), width = "12em") %>% -->
<!--   column_spec(c(4), width = "3em") -->
<!-- ``` -->
\newpage
# Part II. Teaching
The course load for Heilmayr was 3.5 course equivalents per year through the 2021-2022 academic year, and 3 course equivalents per year beginning in the 2022-2023 academic year. Given his split appointment (75% Environmental Studies, 25% Bren), these teaching responsibilities are divided across the two departments. In the 2021-2022 academic year, he was expected to teach 2.625 course equivalents in ES and 0.875 course equivalents in Bren. Beginning in the 2022-2023 academic year, the agreed upon division changed to 2 course equivalents in ES, and 1 course equivalent in ES. 

Heilmayr entered this review period with 0.625 banked course equivalents in ES and 0.17 course equivalents in Bren. In the 2021-2022 academic year, Heilmayr taught 2 course equivalents for Environmental Studies and 1.3  course equivalents for Bren. In the 2022-2023 academic year, Heilmayr taught 2 course equivalents for Environmental Studies and 0.9 course equivalents for Bren. Based on his teaching during this period, and his prior teaching overload, Heilmayr carries forward 0.495 teaching credits towards his future teaching obligations in the Bren School.

## Catalog courses
```{r teaching, echo=FALSE}
teaching %<>%
  mutate("Mean evaluations" = str_c("Q-A: ", teaching$eval_a, "; Q-B: ", teaching$eval_b),
         Course = paste0(Number, ": ", Title),
         "ESCI/Written evals. avail." = ifelse(is.na(eval_a), "No/No", "Yes/Yes")) %>% 
         # ,"ESCI/Written evals. avail." = ifelse(Qtr. == "S20", `ESCI/Written evals. avail.`, paste0(`ESCI/Written evals. avail.`, " COVID-19"))) %>% 
  rename(Enroll. = Enrollment, 
         "Class type" = Type)

teaching %<>%
  filter(review_period==rperiod) %>%
  select(Qtr., Course, "Class type", Units, "Hrs/Week", Enroll., "ESCI/Written evals. avail.")

teaching %>%
  mutate_all(linebreak) %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  column_spec(c(2), width = "17em") %>%
  column_spec(c(7), width = "6em")
```

## Undergraduate advising
``` {r undergrads, echo = FALSE}
students$Name <- paste(students$first_name, ' ', students$last_name)
students$`Optional info` <- students %>% 
  mutate(uni_note = ifelse(Where != "UCSB", Where, NA)) %>%
  select(uni_note, Awards, Notes) %>%
  apply(1, function(x) paste(na.omit(x), collapse=", "))
students <- students %>%
  mutate(start_date = replace(start_date, start_date==end_date, NA))
students$Years <- students %>% 
  select(start_date, end_date) %>%
  apply(1, function(x) paste(na.omit(x), collapse=" - "))
students %<>%
  mutate("Year completed" = replace(end_date, end_date=="present", "Current student"))

undergrads <- students %>%
  filter(Type=="Undergraduate",
         review_period==rperiod) %>%
  rename(Student = Name) %>% 
  select("Student", "Year completed", "Project type", "Optional info")
undergrads %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  column_spec(c(1), width = "8em") %>%
  column_spec(c(2), width = "8em") %>%
  column_spec(c(3), width = "8em") %>%
  column_spec(c(4), width = "17em")
```

## Masters advising
``` {r masters, echo = FALSE}
masters <- students %>%
  filter(Type=="Masters",
         review_period==rperiod) %>%
  rename(Student = Name) %>% 
  select("Student", "Year completed", "Chair/Member", "Optional info")
masters %>%
  kable("latex", booktabs = TRUE, longtable = TRUE) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  column_spec(c(1), width = "8em") %>%
  column_spec(c(2), width = "8em") %>%
  column_spec(c(3), width = "8em") %>%
  column_spec(c(4), width = "17em")
```

## Ph.D. committees
``` {r phds, echo = FALSE}
phds <- students %>%
  filter(Type=="Ph.D.", review_period==rperiod) %>%
  rename(Student = Name) %>% 
  select("Student", "Year completed", "Chair/Member", "Optional info") 
phds %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header")) %>% 
  column_spec(c(4), width = "20em") %>%
  column_spec(c(1), width = "8em") %>%
  column_spec(c(2), width = "8em") %>%
  column_spec(c(3), width = "8em") %>%
  column_spec(c(4), width = "17em")

```

## Postdoctoral scholars supervised
``` {r postdocs, echo = FALSE}
postdocs <- students %>%
  filter(Type=="postdoc", review_period==rperiod) %>%
  select(Name, Years, "Optional info")
postdocs %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  column_spec(c(3), width = "20em")
```

## Other scholars supervised
``` {r scholars, echo = FALSE}
other_scholars <- students %>%
  filter(Type=="other_scholar", review_period==rperiod) %>%
  select(Name, Years, "Project type", "Optional info")
other_scholars %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  column_spec(c(1), width = "8em") %>%
  column_spec(c(2), width = "8em") %>%
  column_spec(c(3), width = "8em") %>%
  column_spec(c(4), width = "17em")
```

## Other teaching contributions
### Conservation Economics Lab meetings
Coordinated a weekly research group seminar series for my lab.

### Bren School group projects
```{r gps, echo=FALSE}
gps %<>%
  filter(review_period==rperiod) %>%
  select(Year, Project, Role)

gps %>%
  mutate_all(linebreak) %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  column_spec(c(2), width = "26em")

```

### Guest lectures
```{r guest_lectures, echo=FALSE}
guest_lectures %<>%
  filter(review_period==rperiod) %>%
  mutate(Class = paste0(Class, ", ", Institution)) %>% 
  select(Year, Class)

guest_lectures %>%
  mutate_all(linebreak) %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header"))
```

<!-- ### Additional mentoring -->
<!-- ```{r add_mentoring, echo=FALSE} -->
<!-- mentoring$Name <- paste(mentoring$first_name, ' ', mentoring$last_name) -->
<!-- mentoring <- mentoring %>% -->
<!--   mutate(end_date = replace(end_date, end_date==start_date, NA)) -->
<!-- mentoring$Years <- mentoring %>%  -->
<!--   select(start_date, end_date) %>% -->
<!--   apply(1, function(x) paste(na.omit(x), collapse=" - ")) -->

<!-- mentoring %<>% -->
<!--   filter(review_period==rperiod) %>% -->
<!--   select(Name, Years, "Optional info") -->

<!-- mentoring %>% -->
<!--   mutate_all(linebreak) %>% -->
<!--   kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "") %>% -->
<!--   kable_styling(latex_options = c("repeat_header")) -->
<!-- ``` -->


# Part III. Professional activities
## Lectures presented
```{r lectures, echo=FALSE}
lectures$`Meeting/Place` <-  apply(lectures %>% select(Organization, Meeting, Location), 1, function(x) paste(na.omit(x), collapse=", "))

lectures <- lectures %>%
  filter(review_period == rperiod) %>%
  select(Date, Title, "Meeting/Place")

lectures %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  column_spec(c(1), width = "8em") %>%
  column_spec(c(2), width = "16em") %>%
  column_spec(c(3), width = "17em")
```

## Grants and contracts
```{r grants, echo=FALSE}
grants <- grants %>% 
  mutate(`Amount (PI share)` = paste0(comma(amount), "\n(", comma(personal_share), ")"),
         end_date = replace(end_date, end_date==start_date, NA))
grants$Years = apply(grants %>% select(start_date, end_date), 1, function(x) paste(na.omit(x), collapse="-"))

grants <- grants %>%
  filter(review_period == rperiod) %>%
  filter(outcome == "Accepted") %>% 
  select(Years, Source, Title, "Amount (PI share)", Role, `New/Cont.`)

grants %>%
  mutate_all(linebreak) %>% 
  kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace", escape = F) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  # kable_styling(latex_options = c("striped")) %>% 
  column_spec(c(1), width = "4em") %>%
  column_spec(c(2), width = "7em") %>%
  column_spec(c(3), width = "13em") %>%
  column_spec(c(4), width = "5em") %>%
  column_spec(c(6), width = "3em")


  # mutate_all(linebreak) %>%
  # kable_styling(latex_options = c("repeat_header")) %>%
  # column_spec(c(1), width = "4em") %>%
  # column_spec(c(2), width = "8em") %>%
  # column_spec(c(3), width = "16em") %>%
  # column_spec(c(4), width = "6em") %>%
  # column_spec(c(6), width = "3em") %>% 
  # kable_styling(latex_options = "striped")

```
<!-- ## Awards and honors -->

<!-- ## Patents -->
<!-- ```{r patents, echo=FALSE} -->
<!-- patents <- patents %>% -->
<!--   filter(review_period == rperiod) %>% -->
<!--   select(Year, Authors, Title, "Patent number") -->

<!-- patents %>% -->
<!--   kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "") %>% -->
<!--   kable_styling(latex_options = c("repeat_header")) %>% -->
<!--   column_spec(c(2), width = "13em") %>% -->
<!--   column_spec(c(3), width = "11em") %>% -->
<!--   column_spec(c(4), width = "10em") -->
<!-- ``` -->


## Reviewing and refereeing activity
``` {r reviewing, echo=FALSE}
reviewing$Activity <- reviewing %>%
  mutate(journal = str_c("\\textit{", reviewing$journal, "}")) %>%
  select(activity, journal, organization) %>%
  apply(1, function(x) paste(na.omit(x), collapse=", "))

reviewing <- reviewing %>% 
  rename(`Number of reviews` = n)
reviewing <- reviewing %>%
  filter(review_period == rperiod) %>%
  select(Date, Activity, `Number of reviews`)

reviewing %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, escape = FALSE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header"))  %>% 
  column_spec(c(1), width = "2em") %>%
  column_spec(c(2), width = "32em") %>%
  column_spec(c(3), width = "6em")
```

## Special appointments
``` {r appointments, echo=FALSE}
appointments <- appointments %>%
  mutate(end_date = replace(end_date, end_date==start_date, NA))
appointments$Years <- apply(appointments %>% select(start_date, end_date), 1, function(x) paste(na.omit(x), collapse="-"))
appointments$`Type of service` <- apply(appointments %>% select(organization, detail), 1, function(x) paste(na.omit(x), collapse=", "))

prof_appointments <- appointments %>%
  filter(review_period == rperiod,
         category == "professional") %>%
  select(Years, Position, "Type of service")

prof_appointments %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  column_spec(c(1), width = "8em") %>% 
  column_spec(c(2), width = "12em") %>% 
  column_spec(c(3), width = "20em") 
```

<!-- ## Other professional contributions -->
<!-- ### Session, workshop and conference organizing -->
<!-- ``` {r organizing, echo=FALSE} -->
<!-- organizing <- organizing %>% -->
<!--   filter(review_period == rperiod) %>% -->
<!--   select(Date, Location, Title, Event, Role) -->

<!-- organizing %>% -->
<!--   kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace") %>% -->
<!--   kable_styling(latex_options = c("repeat_header")) %>% -->
<!--   column_spec(c(1), width = "4em")  %>% -->
<!--   column_spec(c(2), width = "6em")  %>% -->
<!--   column_spec(c(3), width = "12em")  %>% -->
<!--   column_spec(c(4), width = "12em")  %>% -->
<!--   column_spec(c(5), width = "5em")  -->
<!-- ``` -->

# Part IV. Service
## University service
``` {r uni_service, echo=FALSE}
university$`Academic year` <- university %>%
  select(start_date, end_date) %>%
  apply(1, function(x) paste(na.omit(x), collapse="-"))
university$`Type of service` <- apply(university %>% select(department, committee), 1, function(x) paste(na.omit(x), collapse=", "))

university <- university %>%
  filter(review_period == rperiod) %>%
  select("Academic year", Position, "Type of service")

university %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  column_spec(c(3), width = "30em") 
```

## Public service appointments
``` {r public_appointments, echo=FALSE}
public_appointments <- appointments %>%
  filter(review_period == rperiod,
         category == "public") %>%
  select(Years, Position, "Type of service")

public_appointments %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header") )%>%
  column_spec(c(1), width = "8em") %>% 
  column_spec(c(2), width = "12em") %>% 
  column_spec(c(3), width = "20em") 
```

## Public writing
``` {r public_writing, echo=FALSE}
public_writing <- public_writing %>%
  filter(review_period == rperiod) %>% 
  mutate(Year = as.character(Year))

public_writing <- public_writing %>%
  mutate(Title = str_c("``", Title, "''"),
         `Title and authors` = ifelse(is.na(Link),
                                      str_c(Title, ", ", Authors),
                                      str_c("\\href{", Link, "}{", Title, " ", Authors, "}")))


public_writing <- public_writing %>%
  select("Year", "Title and authors", "Outlet", "Category")
public_writing %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, escape = FALSE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  # kable_styling(latex_options = "striped") %>% 
  column_spec(c(1), width = "2em") %>%
  column_spec(c(2), width = "21em") %>%
  column_spec(c(3), width = "8em") %>%
  column_spec(c(4), width = "8em")
```


## Selected public media engagement
``` {r media, echo=FALSE}
# media <- read_csv(paste0(data_dir, '4_service/media.csv'))

media <- media %>%
  filter(review_period == rperiod) %>%
  mutate(Date = as.character(Date))

media <- media %>%
  mutate(Title = str_c("``", Title, "''"))

media$Title <- media %>%
  select(Title, title_note) %>%
  apply(1, function(x) paste(na.omit(x), collapse=", "))

# media <- media %>%
#   mutate(Title = ifelse(is.na(Link), Title, str_c("\\href{", Link, "}{", Title,"}")))


media <- media %>%
  select("Date", "Title", "Outlet")
media %>%
  kable("latex", booktabs = TRUE, longtable = TRUE, linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  column_spec(c(1), width = "6em") %>%
  column_spec(c(2), width = "26em") %>%
  column_spec(c(3), width = "12em")
```

<!-- ## Public service -->
<!-- ``` {r public_service, echo = FALSE} -->
<!-- public$Years <- public %>% -->
<!--   select(start_date, end_date) %>% -->
<!--   apply(1, function(x) paste(na.omit(x), collapse="-")) -->
<!-- public <- public %>% -->
<!--   filter(review_period == rperiod) %>% -->
<!--   select(Years, Position, "Type of service") -->
<!-- public %>% -->
<!--   kable("latex", booktabs = TRUE, longtable = TRUE, escape = FALSE, linesep = "") %>% -->
<!--   kable_styling(latex_options = c("repeat_header")) %>% -->
<!--   column_spec(c(3), width = "30em")  -->
<!-- ``` -->
